---
title: "Basic Report from AEDA"
params:
  data: data
  target: target
---
## This is a first version of a basic report:

```{r, echo = TRUE}
library(rmarkdown, quietly = TRUE)
data = params$data
target = params$target
```


## Running Basic Data Summary 
```{r basicDataSummary, echo = FALSE}
basic.data.sum = basicDataSummary(data = data, target = target)
```
The dataset `r deparse(substitute(data))` contains of `r basic.data.sum$obs` observations and `r basic.data.sum$NAs` missing values. There are `r `
There target column is `r basic.data.sum$data.type.list$target ` and of type `r basic.data.sum$target `
The predictor variables are `r basic.data.sum$data.type.list$X `.  

## Running Missing Value Summary

```{r naSummary, echo = FALSE}
na.summary  = naSummary(data = data)
print(na.summary)
```

```{r NumSum, echo = FALSE}
num.sum.task = makeNumSumTask(id = "basicReportTask", data = data, target = target)
num.sum = makeNumSum(num.sum.task)
#retrieve all columns with summary and the ggplot
num.sum$num.sum
```
